---
title: "orderflowimbalance"
output: pdf_document
date: "2025-01-09"
---

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = "../")  # Set working directory to project root
knitr::opts_knit$set(root.dir = "D:/Python/2025-winter-learn/project")  # Absolute path to project root
```

Import necessary libraries.

```{r}
library(readr)
library(lubridate)
library(dplyr)
library(stargazer)
library(glmnet)
```

# Load data

```{r}
symbols <- c("AAPL", "AMGN", "TSLA", "JPM", "XOM")
#oos_dt_strs <- c(
#  "2024-12-02","2024-12-03","2024-12-04","2024-12-05","2024-12-06",
#  "2024-12-09","2024-12-10","2024-12-11","2024-12-12","2024-12-13",
#  "2024-12-16","2024-12-17","2024-12-18","2024-12-19","2024-12-20",
#  "2024-12-23","2024-12-24",             "2024-12-26","2024-12-27",
#  "2024-12-30","2024-12-31",             "2025-01-02"
#)
is_dt_strs <- c(
  "2024-12-02","2024-12-03","2024-12-04","2024-12-05","2024-12-06",
  "2024-12-09","2024-12-10","2024-12-11","2024-12-12","2024-12-13",
  "2024-12-16","2024-12-17","2024-12-18","2024-12-19","2024-12-20" 
)

is_df <- data.frame()

for (dt_str in is_dt_strs) {
  file_path <- paste0("data/processed/", symbols[1], "_mbp-10_", dt_str, ".csv")
  tmp <- read_csv(file_path, show_col_types = FALSE)
  tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC") 
  date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
  date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
  #interval <- new_interval(date1, date2)
  tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2,]
  
  is_df <- bind_rows(is_df, tmp)
}
colnames(is_df) <- paste0(symbols[1], "_", colnames(is_df))

for (symbol in symbols[2:length(symbols)]) {
  inner <- data.frame()
  for (dt_str in is_dt_strs) {
    file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC") 
    date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
    date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
    #interval <- new_interval(date1, date2)
    tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2,]
    
    inner <- bind_rows(inner, tmp)
  }
  colnames(inner) <- paste0(symbol, "_", colnames(inner))
  #is_df <- cbind(is_df, inner)
  
  # Merge data frames based on the datetime column
  is_df <- merge(is_df, inner, by.x = paste0(symbols[1], "_ts_recv"), by.y = paste0(symbol, "_ts_recv"), all = TRUE)
}
```

```{r}
symbols <- c("AAPL", "AMGN", "TSLA", "JPM", "XOM")

oos_dt_strs <- c(
  "2024-12-23","2024-12-24",             "2024-12-26","2024-12-27",
  "2024-12-30","2024-12-31",             "2025-01-02"
)

oos_df <- data.frame()

for (dt_str in oos_dt_strs) {
  file_path <- paste0("data/processed/", symbols[1], "_mbp-10_", dt_str, ".csv")
  tmp <- read_csv(file_path, show_col_types = FALSE)
  tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC") 
  date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
  date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
  #interval <- new_interval(date1, date2)
  tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2,]
  
  oos_df <- bind_rows(oos_df, tmp)
}
colnames(oos_df) <- paste0(symbols[1], "_", colnames(oos_df))

for (symbol in symbols[2:length(symbols)]) {
  inner <- data.frame()
  for (dt_str in oos_dt_strs) {
    file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC") 
    date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
    date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
    #interval <- new_interval(date1, date2)
    tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2,]
    
    inner <- bind_rows(inner, tmp)
  }
  colnames(inner) <- paste0(symbol, "_", colnames(inner))
  #oos_df <- cbind(oos_df, inner)
  
  # Merge data frames based on the datetime column
  oos_df <- merge(oos_df, inner, by.x = paste0(symbols[1], "_ts_recv"), by.y = paste0(symbol, "_ts_recv"), all = TRUE)
}
```

```{r}
is_df
```

```{r}
oos_df
```


```{r}
interval <- strsplit(colnames(is_df)[3], "_")[[1]][3]
interval
```
## Price Impact of best-level OFIs ( $ \textbf{PI}^{[1]} $ )

```{r}
regress <- function(df, dependent_var, independent_vars) {
  formula <- as.formula(paste(dependent_var, "~", paste(independent_vars, collapse = " + ")))
  model <- lm(formula, data = df)
  return(model)
}
```

Using coefficients from in-sample regression and evaluate on out-of-sample.

```{r}
# Perform regressions for each symbol
for (symbol in symbols) {
  independent_vars <- paste0(symbol, "_ofi_00_", interval)
  # 1. Train the model on IS data
  model <- regress(is_df, paste0(symbol, "_r_", interval), independent_vars)
  print(summary(model))
  # 2. Extract coefficients
  coefs <- coef(model)
  # 3. Predict on OOS data
  complete_cases <- complete.cases(oos_df[, c(paste0(symbol, "_r_", interval), independent_vars)])
  oos_df_complete <- oos_df[complete_cases, ]
  predictions <- coefs[1] + coefs[2] * oos_df_complete[, independent_vars]
  # 4. Evaluate R-squared
  ss_total <- sum((oos_df_complete[, paste0(symbol, "_r_", interval)] - 
                     mean(oos_df_complete[, paste0(symbol, "_r_", interval)]))^2)
  ss_residual <- sum((oos_df_complete[, paste0(symbol, "_r_", interval)] - predictions)^2)
  r_squared <- 1 - (ss_residual / ss_total)
  print(paste("R-squared for", symbol, ":", r_squared)) 
}
```

## Price Impact of Integrated OFIs ( $ \textbf{PI}^{I} $ )

```{r}
# Perform regressions for each symbol
for (symbol in symbols) {
  independent_vars <- paste0(symbol, "_ofi_I_", interval)
  # 1. Train the model on IS data
  model <- regress(is_df, paste0(symbol, "_r_", interval), independent_vars)
  print(summary(model))
  # 2. Extract coefficients
  coefs <- coef(model)
  # 3. Predict on OOS data
  complete_cases <- complete.cases(oos_df[, c(paste0(symbol, "_r_", interval), independent_vars)])
  oos_df_complete <- oos_df[complete_cases, ]
  predictions <- coefs[1] + coefs[2] * oos_df_complete[, independent_vars]
  # 4. Evaluate R-squared
  ss_total <- sum((oos_df_complete[, paste0(symbol, "_r_", interval)] - 
                     mean(oos_df_complete[, paste0(symbol, "_r_", interval)]))^2)
  ss_residual <- sum((oos_df_complete[, paste0(symbol, "_r_", interval)] - predictions)^2)
  r_squared <- 1 - (ss_residual / ss_total)
  print(paste("R-squared for", symbol, ":", r_squared)) 
}
```

```{r}
for (symbol in symbols) {
  # ofi00 to ofi04
  independent_vars <- paste0(symbol, "_ofi_", sprintf("%02d", 0:4), "_", interval)

  model <- regress(is_df, paste0(symbol, "_r_", interval), independent_vars)

  print(summary(model))
}
```

## LASSO for Cross-Impact OFIs (CI)

Before we apply LASSO, we observe that OLS yields non-significant coefficients.

```{r}
for (symbol in symbols) {
  dependent_var <- paste0(symbol, "_r_", interval)
  # ofi00 to ofi04
  independent_vars <- unlist(lapply(symbols, function(symbol) {
    paste0(symbol, "_ofi_", sprintf("%02d", 0:0), "_", interval)
  }))

  model <- regress(is_df, dependent_var, independent_vars)

  print(symbol)
  print(summary(model))
}
```

Regress on the integrated OFIs of all symbols:

```{r}
for (symbol in symbols) {
  # ofi00 to ofi04
  independent_vars <- paste0(symbols, "_ofi_I_", interval)

  model <- regress(is_df, paste0(symbol, "_r_", interval), independent_vars)

  print(summary(model))
}
```

```{r}
for (symbol in symbols) {
  dependent_var <- paste0(symbol, "_r_", interval)
  # ofi00 to ofi04
  independent_vars <- unlist(lapply(symbols, function(symbol) {
    paste0(symbol, "_ofi_", sprintf("%02d", 0:4), "_", interval)
  }))

  model <- regress(is_df, dependent_var, independent_vars)

  print(summary(model))
}
```

We regress the contemporaneous return of AAPL on the self- and cross-impact of the best level OFIs. We apply cross-validation to pick the appropriate parameter for LASSO regression.

```{r}
this_symbol <- "AAPL"
dependent_var <- paste0(this_symbol, "_r_", interval)
independent_vars <- paste0(symbols, "_ofi_00_", interval)

# Prepare data for glmnet
X <- makeX(is_df[, independent_vars], na.impute = TRUE) # Impute missing values in X
y <- is_df[[dependent_var]]

# Perform Lasso regression
model <- cv.glmnet(X, y, alpha = 1, type.measure="mse", family="gaussian")  # alpha = 1 for Lasso
```

The following plot shows three pieces of information. The bottom x-axis is the value of $\log \lambda$. The upper x-axis tells how many non-zero coefficients there are (In this case, the jump from 1 non-zero coefficient to more occurs when $\log\lambda \approx -10$.)

```{r}
fit.lasso = glmnet(X,y)
varnames <- colnames(X)
plot(fit.lasso, xvar="lambda", label=TRUE)
```
The following dataframe shows the first (largest) $\lambda$ that creates an additional nonzero coefficient.

```{r}
df_lambda <- data.frame(
  lambda = model$lambda,
  log_lambda = log(model$lambda),
  n_nonzero_coef = model$nzero
)
df_lambda[diff(df_lambda$n_nonzero_coef) != 0, ]
```
For example, if we pick $\lambda = 6 \times 10^{-5}$, there is only one nonzero coefficient. Moreover, this one is the impact from itself. (Recall that we are regressing on AAPL's return.)

```{r}
model <- glmnet(X, y, alpha = 1, lambda = 6e-5, type.measure="mse", family="gaussian")
coef(model)
```



```{r}
for (this_symbol in symbols) {
  dependent_var <- paste0(this_symbol, "_r_", interval)
  independent_vars <- paste0(symbols, "_ofi_00_", interval)
  
  # Prepare data for glmnet
  X <- makeX(is_df[, independent_vars], na.impute = TRUE)
  y <- is_df[[dependent_var]]
  
  # Perform Lasso regression
  model <- cv.glmnet(X, y, alpha = 1, type.measure = "mse", family = "gaussian")
  
  # Create data frame with lambda, log(lambda), and nzero
  #df_lambda <- data.frame(
  #  lambda = model$lambda,
  #  log_lambda = log(model$lambda),
  #  n_nonzero_coef = model$nzero
  #)
  
  cat(this_symbol, ":", model$lambda.1se, "\n")
  #print(df_lambda[diff(df_lambda$n_nonzero_coef) != 0, ])
  model <- glmnet(X, y, alpha = 1, lambda = model$lambda.1se, type.measure="mse", family="gaussian")
  print(coef(model))
}
```

```{r}
for (this_symbol in symbols) {
  dependent_var <- paste0(this_symbol, "_r_", interval)
  independent_vars <- paste0(symbols, "_ofi_00_", interval)

  # Prepare data for glmnet (IS)
  X_is <- makeX(is_df[, independent_vars], na.impute = TRUE)
  y_is <- is_df[[dependent_var]]

  # Perform Lasso regression
  model <- cv.glmnet(X_is, y_is, alpha = 1, type.measure = "mse", family = "gaussian")
  cat(this_symbol, ":", model$lambda.1se, "\n")
  model <- glmnet(X_is, y_is, alpha = 1, lambda = model$lambda.1se, type.measure="mse", family="gaussian")
  print(coef(model))

  # Predict on IS data and calculate R-squared
  predictions_is <- predict(model, newx = X_is)
  ss_total_is <- sum((y_is - mean(y_is))^2)
  ss_residual_is <- sum((y_is - predictions_is)^2)
  r_squared_is <- 1 - (ss_residual_is / ss_total_is)
  print(paste("IS R-squared for", this_symbol, ":", r_squared_is))

  # Prepare data for glmnet (OOS)
  X_oos <- makeX(oos_df[, independent_vars], na.impute = TRUE) 
  y_oos <- oos_df[[dependent_var]]

  # Predict on OOS data and calculate R-squared
  predictions_oos <- predict(model, newx = X_oos)
  ss_total_oos <- sum((y_oos - mean(y_oos))^2)
  ss_residual_oos <- sum((y_oos - predictions_oos)^2)
  r_squared_oos <- 1 - (ss_residual_oos / ss_total_oos)
  print(paste("OOS R-squared for", this_symbol, ":", r_squared_oos))
}
```

```{r}
for (this_symbol in symbols) {
  dependent_var <- paste0(this_symbol, "_r_", interval)
  independent_vars <- paste0(symbols, "_ofi_I_", interval)

  # Prepare data for glmnet (IS)
  X_is <- makeX(is_df[, independent_vars], na.impute = TRUE)
  y_is <- is_df[[dependent_var]]

  # Perform Lasso regression
  model <- cv.glmnet(X_is, y_is, alpha = 1, type.measure = "mse", family = "gaussian")
  cat(this_symbol, ":", model$lambda.1se, "\n")
  model <- glmnet(X_is, y_is, alpha = 1, lambda = model$lambda.1se, type.measure="mse", family="gaussian")
  print(coef(model))

  # Predict on IS data and calculate R-squared
  predictions_is <- predict(model, newx = X_is)
  ss_total_is <- sum((y_is - mean(y_is))^2)
  ss_residual_is <- sum((y_is - predictions_is)^2)
  r_squared_is <- 1 - (ss_residual_is / ss_total_is)
  print(paste("IS R-squared for", this_symbol, ":", r_squared_is))

  # Prepare data for glmnet (OOS)
  X_oos <- makeX(oos_df[, independent_vars], na.impute = TRUE) 
  y_oos <- oos_df[[dependent_var]]

  # Predict on OOS data and calculate R-squared
  predictions_oos <- predict(model, newx = X_oos)
  ss_total_oos <- sum((y_oos - mean(y_oos))^2)
  ss_residual_oos <- sum((y_oos - predictions_oos)^2)
  r_squared_oos <- 1 - (ss_residual_oos / ss_total_oos)
  print(paste("OOS R-squared for", this_symbol, ":", r_squared_oos))
}
```

```{r}
# # code for one single symbol (IS/OOS)
# interval <- "1min"
# 
# lags <- c(1, 2, 3, 5, 10, 20, 30)
# fwds <- c(1, 2, 3, 5, 10, 20, 30)
# lagcols <- c("ofi_I_1min", paste0("ofi_", sprintf("%02d", 0:4), "_1min"))
# 
# lagged_is_df <- data.frame()
# symbol = symbols[1]
# cols <- paste0(symbol, "_", lagcols)
# for (dt_str in is_dt_strs) {
#   file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
#   tmp <- read_csv(file_path, show_col_types = FALSE)
#   tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC")
#   date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
#   date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
#   tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2, ]
#   colnames(tmp) <- paste0(symbol, "_", colnames(tmp))
# 
#   for (fwd in fwds) {
#     tmp[[paste0(symbol, "_r_", interval, "_fwd", fwd)]] <- lead(tmp[[paste0(symbol, "_r_", interval)]], n = fwd)
#   }
#   for (col in cols) {
#     for (lag in lags) {
#       tmp[[paste0(col, "_lag", lag)]] <- lag(tmp[[col]], n = lag)
#     }
#   }
#   lagged_is_df <- bind_rows(lagged_is_df, tmp)
# }
# 
# lagged_oos_df <- data.frame()
# symbol = symbols[1]
# cols <- paste0(symbol, "_", lagcols)
# for (dt_str in oos_dt_strs) {
#   file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
#   tmp <- read_csv(file_path, show_col_types = FALSE)
#   tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC")
#   date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
#   date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
#   tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2, ]
#   colnames(tmp) <- paste0(symbol, "_", colnames(tmp))
# 
#   for (fwd in fwds) {
#     tmp[[paste0(symbol, "_r_", interval, "_fwd", fwd)]] <- lead(tmp[[paste0(symbol, "_r_", interval)]], n = fwd)
#   }
#   for (col in cols) {
#     for (lag in lags) {
#       tmp[[paste0(col, "_lag", lag)]] <- lag(tmp[[col]], n = lag)
#     }
#   }
#   lagged_oos_df <- bind_rows(lagged_oos_df, tmp)
# }
```

```{r}
lagged_is_df
```

Create look-forward and lagged columns for both IS and OOS and for all symbols.

```{r}
interval <- "1min"
lags <- c(1, 2, 3, 5, 10, 20, 30)
fwds <- c(1, 2, 3, 5, 10, 20, 30)
lagcols <- c("ofi_I_1min", paste0("ofi_", sprintf("%02d", 0:4), "_1min"))

lagged_is_df <- data.frame()
lagged_oos_df <- data.frame()

for (symbol in symbols) {
  cols <- paste0(symbol, "_", lagcols)
  
  inner_is <- data.frame()
  for (dt_str in is_dt_strs) {
    file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC")
    date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
    date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
    tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2, ]
    colnames(tmp) <- paste0(symbol, "_", colnames(tmp))

    for (fwd in fwds) {
      tmp[[paste0(symbol, "_r_", interval, "_fwd", fwd)]] <- lead(tmp[[paste0(symbol, "_r_", interval)]], n = fwd)
    }
    for (col in cols) {
      for (lag in lags) {
        tmp[[paste0(col, "_lag", lag)]] <- lag(tmp[[col]], n = lag)
      }
    }
    inner_is <- bind_rows(inner_is, tmp)
  }
  if (nrow(lagged_is_df) == 0) {
    lagged_is_df <- inner_is
  } else {
    lagged_is_df <- merge(lagged_is_df, inner_is, by.x = paste0(symbols[1], "_ts_recv"), by.y = paste0(symbol, "_ts_recv"), all = TRUE)
  }

  inner_oos <- data.frame()
  for (dt_str in oos_dt_strs) {
    file_path <- paste0("data/processed/", symbol, "_mbp-10_", dt_str, ".csv")
    tmp <- read_csv(file_path, show_col_types = FALSE)
    tmp$ts_recv <- as.POSIXct(tmp$ts_recv, tz = "UTC")
    date1 <- as.POSIXct(paste0(dt_str, " ", "14:45:00"), tz = "UTC")
    date2 <- as.POSIXct(paste0(dt_str, " ", "20:45:00"), tz = "UTC")
    tmp <- tmp[tmp$ts_recv >= date1 & tmp$ts_recv <= date2, ]
    colnames(tmp) <- paste0(symbol, "_", colnames(tmp))

    for (fwd in fwds) {
      tmp[[paste0(symbol, "_r_", interval, "_fwd", fwd)]] <- lead(tmp[[paste0(symbol, "_r_", interval)]], n = fwd)
    }
    for (col in cols) {
      for (lag in lags) {
        tmp[[paste0(col, "_lag", lag)]] <- lag(tmp[[col]], n = lag)
      }
    }
    inner_oos <- bind_rows(inner_oos, tmp)
  }
  if (nrow(lagged_oos_df) == 0) {
    lagged_oos_df <- inner_oos
  } else {
    lagged_oos_df <- merge(lagged_oos_df, inner_oos, by.x = paste0(symbols[1], "_ts_recv"), by.y = paste0(symbol, "_ts_recv"), all = TRUE)
  }
}

# Set "AAPL_ts_recv" as index column for lagged_is_df
rownames(lagged_is_df) <- lagged_is_df$AAPL_ts_recv
lagged_is_df$AAPL_ts_recv <- NULL  # remove the original column
rownames(lagged_oos_df) <- lagged_oos_df$AAPL_ts_recv
lagged_oos_df$AAPL_ts_recv <- NULL # remove

lagged_is_df <- na.omit(lagged_is_df)
lagged_oos_df <- na.omit(lagged_oos_df)
```

```{r}
lagged_is_df
```

```{r}
# lasso_lagged_regress <- function(is_df, dependent_var, independent_vars, lags = c(1, 2, 3, 5, 10, 20, 30), fwd = 1) {
#   # Construct lagged variable names
#   lagged_vars <- paste0(rep(independent_vars, each = length(lags)), "_lag", rep(lags, length(independent_vars)))
# 
#   # Prepare data for glmnet
#   X <- as.matrix(is_df[, lagged_vars])
#   y <- is_df[[paste0(dependent_var, "_fwd", fwd)]]
# 
#   # Perform Lasso regression
#   model <- glmnet(X, y, alpha = 1, lambda = 5e-06)  # alpha = 1 for Lasso
# 
#   return(model)
# }
# 
# this_symbol <- "AAPL"
# independent_vars <- paste0(this_symbol, "_ofi_00_", interval)
# model <- lasso_lagged_regress(lagged_df, paste0(this_symbol, "_r_", interval), independent_vars)
# 
# # Print coefficients
# coef(model) 
```

```{r}

# Loop through all symbols
for (this_symbol in symbols) {
  independent_vars <- paste0(this_symbol, "_ofi_00_", interval, "_lag1")
  # Perform OLS regression on IS data
  model <- regress(lagged_is_df, paste0(this_symbol, "_r_", interval), independent_vars)

  # Print IS R-squared
  print(summary(model)) 

  # Calculate OOS R-squared
  predictions_oos <- predict(model, newdata = lagged_oos_df)  # Predict on OOS data
  ss_total_oos <- sum((lagged_oos_df[[paste0(this_symbol, "_r_", interval)]] - mean(lagged_oos_df[[paste0(this_symbol, "_r_", interval)]]))^2)
  ss_residual_oos <- sum((lagged_oos_df[[paste0(this_symbol, "_r_", interval)]] - predictions_oos)^2)
  r_squared_oos <- 1 - (ss_residual_oos / ss_total_oos)
  print(paste("OOS R-squared for", this_symbol, ":", r_squared_oos))
}
```


```{r}
lasso_lagged_regress <- function(is_df, oos_df, dependent_var, independent_vars, lags = c(1, 2, 3, 5, 10, 20, 30), fwd = 1) {
  # Construct lagged variable names
  lagged_vars <- paste0(rep(independent_vars, each = length(lags)), "_lag", rep(lags, length(independent_vars)))

  # Prepare data for glmnet (IS)
  X_is <- as.matrix(is_df[, lagged_vars])
  y_is <- is_df[[paste0(dependent_var, "_fwd", fwd)]]

  # Perform Lasso regression with cross-validation
  model_cv <- cv.glmnet(X_is, y_is, alpha = 1, type.measure = "mse", family = "gaussian") 
  # model <- glmnet(X_is, y_is, alpha = 1, lambda = model_cv$lambda.1se, type.measure="mse", family="gaussian")
  model <- glmnet(X_is, y_is, alpha = 1, lambda = model_cv$lambda.1se, type.measure="mse", family="gaussian")

  # Predict on IS data and calculate R-squared
  predictions_is <- predict(model, newx = X_is)
  ss_total_is <- sum((y_is - mean(y_is))^2)
  ss_residual_is <- sum((y_is - predictions_is)^2)
  r_squared_is <- 1 - (ss_residual_is / ss_total_is)
  print(paste("IS R-squared for", dependent_var, ":", r_squared_is))

  # Prepare data for glmnet (OOS)
  X_oos <- as.matrix(oos_df[, lagged_vars])
  y_oos <- oos_df[[paste0(dependent_var, "_fwd", fwd)]]

  # Predict on OOS data and calculate R-squared
  predictions_oos <- predict(model, newx = X_oos)
  ss_total_oos <- sum((y_oos - mean(y_oos))^2)
  ss_residual_oos <- sum((y_oos - predictions_oos)^2)
  r_squared_oos <- 1 - (ss_residual_oos / ss_total_oos)
  print(paste("OOS R-squared for", dependent_var, ":", r_squared_oos))

  return(model)
}

ols_lagged_regress <- function(is_df, oos_df, dependent_var, independent_vars, lags = c(1, 2, 3, 5, 10, 20, 30), fwd = 1) {
  # Construct lagged variable names
  lagged_vars <- paste0(rep(independent_vars, each = length(lags)), "_lag", rep(lags, length(independent_vars)))

  # Prepare data for lm (IS)
  X_is <- is_df[, lagged_vars]
  y_is <- is_df[[paste0(dependent_var, "_fwd", fwd)]]

  # Perform OLS regression
  model <- lm(y_is ~ ., data = X_is)  # Use "." to include all lagged_vars

  # Predict on IS data and calculate R-squared
  predictions_is <- predict(model, newdata = X_is)
  ss_total_is <- sum((y_is - mean(y_is))^2)
  ss_residual_is <- sum((y_is - predictions_is)^2)
  r_squared_is <- 1 - (ss_residual_is / ss_total_is)
  print(paste("IS R-squared for", dependent_var, ":", r_squared_is))

  # Prepare data for lm (OOS)
  X_oos <- oos_df[, lagged_vars]
  y_oos <- oos_df[[paste0(dependent_var, "_fwd", fwd)]]

  # Predict on OOS data and calculate R-squared
  predictions_oos <- predict(model, newdata = X_oos)
  ss_total_oos <- sum((y_oos - mean(y_oos))^2)
  ss_residual_oos <- sum((y_oos - predictions_oos)^2)
  r_squared_oos <- 1 - (ss_residual_oos / ss_total_oos)
  print(paste("OOS R-squared for", dependent_var, ":", r_squared_oos))

  return(model)
}

# Loop through all symbols
for (this_symbol in symbols) {
  independent_vars <- paste0(this_symbol, "_ofi_00_", interval)
  # model <- lasso_lagged_regress(lagged_is_df, lagged_oos_df, paste0(this_symbol, "_r_", interval), independent_vars)
  model <- ols_lagged_regress(lagged_is_df, lagged_oos_df, paste0(this_symbol, "_r_", interval), independent_vars)

  # Print coefficients
  # print(coef(model))
  print(summary(model))
}
```


```{r}
for (this_symbol in symbols) {
  independent_vars <- paste0(this_symbol, "_ofi_00_", interval)
  model <- lasso_lagged_regress(lagged_is_df, lagged_oos_df, paste0(this_symbol, "_r_", interval), independent_vars)

  # Print coefficients
  print(coef(model))
}
```

```{r}
for (this_symbol in symbols) {
  independent_vars <- paste0(symbols, "_ofi_00_", interval)
  model <- lasso_lagged_regress(lagged_is_df, lagged_oos_df, paste0(this_symbol, "_r_", interval), independent_vars)

  # Print coefficients
  print(coef(model))
}
```

```{r}
for (this_symbol in symbols) {
  independent_vars <- paste0(this_symbol, "_ofi_I_", interval)
  model <- lasso_lagged_regress(lagged_is_df, lagged_oos_df, paste0(this_symbol, "_r_", interval), independent_vars)

  # Print coefficients
  print(coef(model))
}
```